### 2013-12-30 mcmc.tex
diy advice

...Why everyone reading this document should stop here and JUST FREAKIN' CODE THIS UP.

>>>>

As we mention below,
  there are many MCMC methods more advanced than M--H.
However, they all share characteristics with M--H,
  such that it is very valuable to understand M--H well before using anything more advanced.
Furthermore, a scientist new to MCMC benefits enormously from
  building, tuning, and using her or his own MCMC software.
One piece of advice we give then,
  to the new user of MCMC,
  is to code up, tune, and use a M--H MCMC sampler for a scientific project.
A huge amount is learned in doing this,
  and it is very often the case that the home-built M--H MCMC does everything needed;
  you often don't need any more advanced tool.
Only after you have concluded that your home-built M--H MCMC sampler
  is not suited to your project
  (or not developed properly into a properly versatile software package)
  should you download and start to use any professionally developed alternative.
That is, even if---in the end---%
  you want to leave the sampling code to the experts and run an industrial-strength code,
  it is still valuable to build your own,
  given the simplicity of the algorithm,
  and given the intuition you gain by doing it (at least once) yourself.
